timesliced_random_cell_selection

### 2018-11-02 src/raster_sjl.Rmd
messing with if statement in loop... not working...

```{r}
#Data_Loop <-NULL #Gonna put my loop data in here
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  de <- obssp$depth[[i]]  #have a variable for the depth layer
  #print(de)
  obssp$samtest[i] <- extract(x=rasbr_aea[[de]], y = obssp) #this is the equation you will be calculating for every value of y

  #print the i value so you can track progress. Good for longer loops
  print(i)
  #Close the loop
}
#Data_Loop
obssp$samtest
obssp
```

@@

Ok next step, can you dynamically name the column with the variable in question (or at least the name of the original netcdf)

>>>>

```{r}
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  de <- obssp$depth[[i]]  #have a variable for the depth layer
  obssp$salinity_depth[i] <- extract(x=rasbr_aea[[de]], y = obssp) #this is the equation you will be calculating for every value of y
  obssp$salinity_surface[i] <- extract(x=rasbr_aea[[1]], y = obssp) #this is the equation you will be calculating for every value of y
  print(i)
}
obssp$salinity_depth
obssp$salinity_surface
```

@@

test with just extracting the surface layer data..

```{r}
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  obssp$testsurface[i] <- extract(x=rasbr_aea[[1]], y = obssp) #this is the equation you will be calculating for every value of y
  print(i)
  }
obssp$salinity_surface
obssp
```

scrap the variable name matching idea (instead just make a loop for each variable, and each variable held in a different folder). just try select by year and month.
note you have changed the dates on the .csv file so reload it

```{r warning=FALSE}
obs <- read.csv("../data/observations3.csv", header = TRUE) #change this path to your .csv location
obs$month <- sprintf("%02d",obs$month) # new addition to add the 0 infront of single digit... test for seeing if you can match the netcdf name for year month selection of bricks
xy <- obs[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
obssp <- SpatialPointsDataFrame(coords = xy, data = obs, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.

#the loop....
netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf){  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working on
  brkyr <- sapply(strsplit(netcdf_name[i], "_"), "[[", 1) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- sapply(strsplit(netcdf_name[i], "_"), "[[", 2) # extracting the second part of the netcdf filename (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:length(obssp)) {  
      print(j)
      de <- obssp$depth[[j]]  # a variable for the observation depth layer
      yr <- obssp$year[j]  # a variable for the observation year
      mth <- obssp$month[j]  # a variable for the observation month
      #I think i need an if statement here... if brkyr == yr & brkmth == mth do the data extraction below
        if (brkyr == yr & brkmth == mth){
          obssp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = obssp) 
          obssp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = obssp)

        }
    }
}
obssp$salinity_depth
obssp$salinity_surface
```
not extracting the correct values...

check

load in the three netcdfs
```{r}
nc1 <-  "../data/env/testnetcdf/salinity/1993_01_salinity.nc" # change the file path to where ever your netcdfs are saved
row1rast <- brick(nc1,lvar = 4) #lvar = 4 is used because the netCDF contains four dimensions. Without this command, the raster brick will only have one level (the top one, which is my surface data)
nc2 <-  "../data/env/testnetcdf/salinity/1998_01_salinity.nc" # change the file path to where ever your netcdfs are saved
row2rast <- brick(nc2,lvar = 4) #lvar = 4 is used because the netCDF contains four dimensions. Without this command, the raster brick will only have one level (the top one, which is my surface data)
nc3 <-  "../data/env/testnetcdf/salinity/1998_02_salinity.nc" # change the file path to where ever your netcdfs are saved
row3rast <- brick(nc3,lvar = 4) #lvar = 4 is used because the netCDF contains four dimensions. Without this command, the raster brick will only have one level (the top one, which is my surface data)
```

let's get the values manually at depth
```{r}
testrow1 <- read.csv("../data/row1.csv", header = TRUE)
testrow1$month <- sprintf("%02d",testrow1$month)
testrow1xy <- testrow1[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow1sp <- SpatialPointsDataFrame(coords = testrow1xy, data = testrow1, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow1sp
test15 <- extract(x=row1rast[[15]], y = testrow1sp)
test15
testrow2 <- read.csv("../data/row2.csv", header = TRUE)
testrow2$month <- sprintf("%02d",testrow2$month)
testrow2xy <- testrow2[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow2sp <- SpatialPointsDataFrame(coords = testrow2xy, data = testrow2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow2sp
test22 <- extract(x=row2rast[[22]], y = testrow2sp)
test22
testrow3 <- read.csv("../data/row3.csv", header = TRUE)
testrow3$month <- sprintf("%02d",testrow3$month)
testrow3xy <- testrow3[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow3sp <- SpatialPointsDataFrame(coords = testrow3xy, data = testrow3, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow3sp
test17 <- extract(x=row3rast[[17]], y = testrow3sp)
test17
```

let's get the values manually at the surface
```{r}
testrow1.1 <- extract(x=row1rast[[1]], y = testrow1sp)
testrow1.1
testrow2.1 <- extract(x=row2rast[[1]], y = testrow2sp)
testrow2.1
testrow3.1 <- extract(x=row3rast[[1]], y = testrow3sp)
testrow3.1
```
